### 2016-11-04 final_checks/DVCS-CAN-Meeting-Comments.tex
update the direcotry with the final check results regarding the missing energy binning

\section*{\centering{Answers to the final questions sent on October 7th, 2016}}

@@

\newpage
    \begin{figure}[tbp]
   \includegraphics[height=6.0cm]{fig/new_ME_Coh_bins.png}
   \includegraphics[height=6.0cm]{fig/e4Hegamma_e4Hepi0_Phi_ME.png}
   \hspace{-3.0cm} \includegraphics[height=6.5cm]{fig/new_BSA_coherent_ME.png}
   \hspace{-1.0cm} \includegraphics[height=6.5cm]{fig/new_coh_ME_alpha.png}
   \caption{from top to bottom and from left to right, coherent missing energy 
      binning, the corresponding background acceptance ratio from simulation, 
      the reconstructed beam-spin asymmetries as a function of $\phi$ (middle), 
   and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
asymmetries as a function of the mean missing energy in each bin.  }
   \label{fig:coherent_ME_bins_2}
    \end{figure}
\end{enumerate}

@@

In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
uncertainties. For instance, regarding the bin extraction from the source 'data 
binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
is calculated as the difference between the two reconstructed asymmetries.  
Similar procedures have been carried out for the other studies, and finally all 
the contributions were added quadratically. These systematic uncertainties will 
be shown with the final asymmetry results in the following chapter.

>>>>

\section*{\centering{Answers to the final questions sent on October 10th, 
2016}}

@@

    \begin{figure}[tbp]
     \centering
       \includegraphics[height=6.5cm]{fig_new/e4Hegamma_e4Hepi0_Phi_ME.png}
       \includegraphics[height=6.5cm]{fig_new/BSA_coherent_ME.png}
       \includegraphics[height=6.5cm]{fig_new/coh_ME_alpha.png}
   \caption{From top to bottom, the corresponding background acceptance ratio 
in the different missing energy bins, the reconstructed beam-spin asymmetries 
as a function of $\phi$ (middle), and the extracted asymmetry at $\phi = 90 
^{\circ}$ from fitting the asymmetries as a function of the mean missing energy 
in each bin.}
   \label{fig:coherent_ME_bins_2}
    \end{figure}

 \item Regarding the request of cutting the tails and comparing the 
reconstructed coherent asymmetries to the ones without cutting the tails, the 
asymmetries are presented in fig \ref{fig:BSA_ME_bins_sig} as a function of 
$\phi$ in bins in $Q^{2}$, $x_{B}$ and $-t$. The $Q^{2}$, $x_{B}$ and $-t$ 
dependences of $A_{LU}$ at $\phi = 90 ^{\circ}$, from fitting the signals in 
fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{ig:ALU_ME_bins_sig} 
with and without cutting the tails in the missing energy distribution.  One can 
conclude that the two sets are compatible within the given error bars.

    \begin{figure}[tbp]
     \centering
       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_Q2_ME.png}
       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_xB_ME.png}
       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_t_ME.png}
   \caption{From top to bottom, the reconstructed beam-spin asymmetries as a 
      function of $\phi = 90 ^{\circ}$ in $Q^{2}$,
$x_{B}$ and $-t$ with cutting the tails in red and without cutting the tails in 
blue.  }
   \label{fig:BSA_ME_bins_sig}
    \end{figure}

    \begin{figure}[tbp]
     \centering
       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_Q2.png}
       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_xB.png}
       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_t.png}
       \caption{The extracted asymmetry at $\phi = 90 ^{\circ}$ from
          fitting the asymmetries in fig \ref{fig:BSA_ME_bins_sig} as a 
       function of $Q^{2}$, $x_{B}$ and $-t$ with cutting the tails in red and 
    without cutting the tails in blue.  }
   \label{fig:ALU_ME_bins_sig}
    \end{figure}

@@

In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
uncertainties. For instance, regarding the bin extraction from the source 'data 
binning' listed in table 4.2, the uncertainty is calculated as the difference 
between the two reconstructed asymmetries.  Similar procedures have been 
carried out for the other studies, and finally all the contributions were added 
quadratically. These systematic uncertainties will be shown with the final 
asymmetry results in the following chapter.
